Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life

### 2022-03-21 output/paper3.Rmd
fix grammar

---
title: "Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and less working hours feel happier about life, while married peole of older age with less income and less working hours and higher education level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

# Introduction
Different aspects of the Canadian society has entered a relatively stable stage in the past few decades, such as its economy and politics. However, it doesn’t mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles. Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage and forming family. Surveys have shown that more than half of the Canadians see no reasons in getting legally married [@citeintro]. They tend to form common low relationships or simply stay single, because from their perspectives, it seemed like marriages are more likely to end up in a mess than happiness.

@@

A supplementary survey is provided in the Appendix in section \@ref(supplementary-survey) that incorporate the main focus of this paper and the general social survey. It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.

@@

Figure \@ref(fig:figure3) indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively. It is not hard to observe that the group of singles generally has a lower income level than the group of married people. In addition, by comparing within single respondents, it is interesting to find out that people with lower income levels feel better about their lives than people with higher income levels. This implies that personal income actually may have a considerable impact on the single people's feeling about life. For the married people, it seems like income level has no significant correlation with their feelings about life; a considerable number of respondents who earn less than \$25000 a year rated their feelings at a score of 10, while some respondents that earn over \$100000 a year only rated their feelings at a score of 8.

@@

Figure \@ref(fig:figure5) shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people. For married people, it seems that higher education level may lead to higher scores of feelings about life. Most of the married respondents with bachelor's degree or college certificate give higher scores of 8 or more on feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.

@@

In section \@ref(age-vs-feelings-about-life), we’ve discussed that older people with families tend to feel better about their lives compared to younger age groups, and at the same time, younger people that have not yet form families also tend to feel better about their lives when comparing to single elderly people. One possible explanation for this particular result is difference between young and old people in terms of their ideology, health conditions, and social status. Family would be a strong support for the elders who have high risks to experience illnesses, social isolation, and financial crisis. The younger generations, on the other hand, who are more capable of overcoming the crisis faced by the elders, often value the importance of having personal space and feeling controlled of their own lives more. Family has both advantages and drawbacks from looking at these two perspectives, so it’s not surprised that Canadians have such diverse attitudes towards family.

@@

From our perspective, it might be tempting to assume that people with higher incomes are likely to be happier because they have more purchasing power and higher consumption levels, making it easier for them to buy things than ordinary people who have to take a long time to save up for.
However, in this paper, it’s quite surprising to find that people who are married with extremely high income tend to be less happy than people who earn less. After consideration and discussion, the possible reasons are as follows:

On one hand, people who have been married have more pressure about their family, not only the family daily expenses, but also a large proportion of possible expenses from raising children. For them, a large part of the high salary earned by hard work every day is for family expenses, and there may even be a feeling of being on the run all the time, which makes them feel less happy with life.

On the other hand, people who are single right now spend most of their salary on themselves, no matter they go out to eat, drink or buy things for themselves. There is less pressure, so they are more likely to feel satisfied and happy about life.

>>>>

---
title: "Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and more working hours feel happier about life, while married peole of older age with less working hours and higher educational level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

# Introduction
Different aspects of the Canadian society has entered a relatively stable stage in the past few decades, such as its economy and politics. However, it does not mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles. Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage and forming family. Surveys have shown that more than half of the Canadians see no reasons in getting legally married [@citeintro]. They tend to form common low relationships or simply stay single, because from their perspectives, it seemed like marriages are more likely to end up in a mess than happiness.

@@

A supplementary survey is provided in the Appendix in section \@ref(supplementary-survey) that incorporate the main focus of this paper and the general social survey. It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigations on this topic.

@@

Figure \@ref(fig:figure3) indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively. It is not hard to observe that the group of singles generally has a lower income level than the group of married people. In addition, by comparing within single respondents, it is interesting to find out that people with lower income levels feel better about their lives than people with higher income levels. This implies that personal income actually may have a considerable impact on the single people's happiness. For the married people, it seems like income level has no significant correlation with their feelings about life; a considerable number of respondents who earn less than \$25000 a year rated their feelings at a score of 10, while some respondents that earn over \$100000 a year only rated their feelings at a score of 8.

@@

Figure \@ref(fig:figure5) shows that, education level has some effect on the married respondents' feelings about life while it has little influence on the single respondents. For married people, it seems that higher education level may lead to higher scores of feelings about life. Most of the married respondents with bachelor's degree or college certificate give higher scores of 8 or more on feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.

@@

In section \@ref(age-vs-feelings-about-life), we’ve discussed that older people with families tend to feel better about their lives compared to younger age groups, and at the same time, younger people that have not yet form families also tend to feel better about their lives when comparing to single elderly people. One possible explanation for this particular result is difference between young and old people in terms of their ideology, health conditions, and social status. Family would be a strong support for the elders who have high risks to experience illnesses, social isolation, and financial crisis. The younger generations, on the other hand, who are more capable of overcoming the crisis faced by the elders, often value the importance of having personal space and feeling controlled of their own lives more. Family has both advantages and drawbacks from looking at these two perspectives, so it’s not surprised that Canadians of different age groups have such diverse attitudes towards family.

@@

From our perspective, it might be tempting to assume that people with higher incomes are likely to be happier because they have more purchasing power and higher consumption levels, making it easier for them to buy things than ordinary people who have to take a long time to save up for.
However, in this paper, it’s quite surprising to find that married respondents with extremely high income tend to be less happy than people who earn less, and similarly, single respondents who earn lower wages also rate their feelings high. After consideration and discussion, the possible reasons are as follows:

People who have been married have more pressure about their family, not only the family daily expenses, but also a large proportion of possible expenses from raising children. For them, a large part of the high salary earned by hard work every day is for family expenses, and there may even be a feeling of being on the run all the time, which is not contributing positively to their feelings about life.

People who are single right now spend most of their salary on themselves, no matter they go out to eat, drink or buy things for themselves. There is less pressure, so they are more likely to feel satisfied and happy about life.
